### 2014-11-10 evaluation.tex

\item \textbf{RUBiS}: An ebay-like auction site~\cite{RUBiS}. The
  application allows users to browse items, bid for items on sale, and pay
  for items from a wallet modelled after a bank account.

\item \textbf{Microblog}: A twitter-like microblogging site, modelled after
  Twissandra~\cite{Twissandra}. The application allows adding new users,
  adding and replying to tweets, following, unfollowing and blocking users,
  and fetching a user's timeline, userline, followers and following.
\end{itemize}

>>>>

\item \textbf{RUBiS}: An eBay-like auction site~\cite{RUBiS}. The
  application allows users to browse items, bid for items on sale, and pay
  for items from a wallet modeled after a bank account.

\item \textbf{Microblog}: A twitter-like microblogging site, modeled after
  Twissandra~\cite{Twissandra}. The application allows adding new users,
  adding and replying to tweets, following, unfollowing and blocking users,
  and fetching a user's timeline, userline, followers and following.
\end{itemize}
